Synpotic Soil Characterization

### 2025-08-12 3-reports/manuscript_figures.Rmd
add soil moisture sensors to targets and Rmd

```{r}
source("2-code/0-packages.R")
library(ggbiplot)
library(targets)

@@

```{r targets}
targets::tar_load(c(data_combined, sample_key))
```

@@

>>>>

```{r}
source("2-code/0-packages.R")
library(ggbiplot)
library(targets)
library(ggh4x)

@@

```{r targets}
targets::tar_load(c(data_combined, sample_key))
targets::tar_load_everything()
```

@@

## SOIL MOISTURE SENSORS

Processed data are available here in this repository. Raw data are available on Google Drive (access needed).

### Soil water content for 2022-23

```{r gg_vwc, fig.height=8, fig.width=10}
# plot vwc

vwc_data %>% 
  filter(value > 0) %>% 
  reorder_site() %>% 
  reorder_transect() %>% 
  ggplot(aes(x = datetime_est, y = value, color = transect))+
  geom_line()+
  #  facet_wrap(~ site + transect)+
  facet_nested_wrap(~region + site,
                    nest_line = element_line(colour = "grey")) +
  scale_color_manual(breaks = c("upland", "transition", "wte", "wetland"), 
                     values = pal_transect)+
  labs(x = "", 
       y = "Water content (% v/v)",
       color = "")+
  theme_kp()+
  theme(axis.text.x = element_text(size = 14, angle = 45, hjust = 1),
        panel.grid = element_blank())

### Summarized soil water content

```{r}
vwc_means %>% knitr::kable()
```

### Water level in soil

When water level is positive (above surface), it means the soil is flooded.

```{r gg_water_level, fig.height=8, fig.width=10}

troll %>% 
  ggplot(aes(x = datetime_est, y = wl_below_surface_m, color = transect))+
  geom_hline(yintercept = 0, alpha = 0.8)+
  geom_line(aes(y = rollmean), linewidth = 1)+
  facet_nested_wrap(~region + site,
                    nest_line = element_line(colour = "grey"))+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "wetland"), 
                     values = pal_transect)+
  labs(x = "",
       y = "Water level below surface (m)",
       color = "")+
  theme_kp()+
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(size = 14, angle = 45, hjust = 1))   ##

### Water table summary

```{r}
water_table %>% knitr::kable()
```

### Calculating time flooded (% of the year)

```{r}
percent_flooded %>% knitr::kable()
```
